\chapter{Text Datasets}
\label{chap:appendix_datasets}

Here is the list of all the datasets created as part of this thesis.

\begin{enumerate}[label=\textbf{A.\arabic*}]
\item\label{item:comarg} \ComArg is a dataset of online user comments manually annotated with
comment-argument pairs. The dataset is created for the argument
recognition task: identifying what arguments, from a predefined
set of arguments, have been used in users' comments, and how.
It consists of 1285 and 1013 comment-argument pairs from 
on-line discussions of \emph{Gay Marriages} (GM) 
and \emph{Under God in pledge} (UGIP) respectively.
The dataset is publicly available at:
\url{http://takelab.fer.hr/data/comarg/}

\item\label{item:argpremises} ArgPremises is a dataset of 
implicit premises manually annotated on matching claims. 
The dataset is created to explore what are the implied premises users 
make when expressing support for a claim.
Additionally, it was used to help solve the claim matching task; 
using implicit premise information whilst 
identifying whether a pair of claims expresses the same argument. 
It consists of 494 claim pairs and 3977 respective premises on topics
of \emph{Marijuana Legalization} (MA), \emph{Gay Rights} (GA), 
\emph{Abortion Legalization} (AB),
and \emph{Obama Presidency} (OB).
The dataset is publicly available at:
\url{http://takelab.fer.hr/data/argpremises/}

\item\label{item:microstructures_dataset} 
The Claim Microstructure dataset contains online
discussion comments split into claim
segments, translated into claim microstructures. The dataset is created
to explore how claims can be structured using a restricted
language and grammar. Additionally, it was used to help solve
the stance classification task; using claim microstructure
information when determining stance of a claim. 
The dataset consists of 
100 user posts on the ``\emph{Gay Rights}'' (GA) topic, 
split into 920 claim segments and paraphrases, which two people
(A1 and A2) annotated
882 microstructures (A1) and 842 microstructures (A2), and a hierarchical 
list of 307 concepts used to form microstructures. 
The dataset is publicly available at:
\url{http://takelab.fer.hr/claim-micro}

\item\label{item:structure_dataset} 
Similarly to the microstructure dataset, 
the ontology formalization dataset also contains online discussion
comments split into claims and translated to claim formalizations.
The claim formalizations are logical representations of claims
and may be used to logically derive implicit claims.
The formalization is defined by a two-level ontology: an upper and 
a domain ontology. 
The dataset consists of 100 user comments on the ``\emph{Marijuana}''
split into 920 claim segments and paraphrases. 
The domain ontology for the topic consists of 75 domain
individuals. Three people annotated the claim segments with 
864 (A1), 867 (A2), and 860 (A3) claim individual formalizations.

\end{enumerate}
