\chapter{Annotation Guidelines}
\label{chap:annotation_guidelines}

Quality labelled annotated datasets are essential to build and evaluate argumentation
mining models.  High quality dataset annotation requires that annotators are
well trained in the task at hand. 
Data should be consistently annotated between indepedently working annotators. 
To ensure annotators understand the assigment and are able to complete 
the annotation task successfully, good annotation guidelines are required. 
During the annotation of data described in this thesis  
annotators had to do a test annotation before the real one, 
discuss differences until resolution, and redo annotation of examples
where there was no consensus. 
Once the annotation is complete, we measure inter-annotator agreement. 
In the case of two annotators that each classify $N$ items into $k$ mutually
exclusive categories, we use the Cohen's kappa \citep{cohen1960coefficient}. 
Cohen's kappa is defined as
$$
\kappa = \frac{p_0 - p_e}{1 - p_e}
$$
where $p_0$ is the relative observed agreement among annotators, and 
$p_e$ is the hypothetical probability of chance agreement. 
We use Fleiss' kappa to asses inter-annotator agreement when dealing with more than
two annotators \citep{fleiss1993review}.
Let $N$ be the number of annotators, $n$ number of ratings per subject, and
$k$ number of categories into which assignments are made. Then $n_{ij}$ represents
the number of annotators who assigned $i$-th subject to the $j$-th category. 
Fleiss' kappa is defined the same as Cohen's kappa, but $p_0$ and $p_e$ are defined as:
\begin{align*}
p_0 &= \frac{1}{Nn(n-1)} \left( \sum_{i=1}^{N} \sum_{j=1}^{k} n_{ij}^2 - Nn \right) \\
p_e &= \frac{1}{Nn} \sum_{j=1}^{k} \left( \sum_{i=1}^{N} n_{ij} \right)^2
\end{align*}

This chapter shows the annotation guidelines for 
\begin{enumerate*}[label=(\arabic*)]
\item microstructures (Section~\ref{sec:microstructure_annotation_appendix}), 
\item argumentative segments (Section~\ref{sec:argseg_annotation}),
\item prominent claim and claim relationship pairs (Section~\ref{sec:argrec_annotation}),
\item claim set similarities, (Section~\ref{app:sec:argpremises_annotation}), and
\item claim formalizations (Section~\ref{sec:formalization_annotation}).
\end{enumerate*}

\input{910_microstructure_annotation.tex}

\input{911_argumentative_segment_annotation.tex}

\input{912_argrec_annotation.tex}

\input{913_argpremises_annotation.tex}

\input{914_formalizations_annotation.tex}

